---
title: "Makeup Shades"
author: "Yuzhou Pan"
date: "2021-04-01"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plot

```{r, message=FALSE, error=FALSE, include=FALSE, warning=FALSE}
sephora <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/sephora.csv')
ulta <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/ulta.csv')
allCategories <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allCategories.csv')
allShades <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allShades.csv')
allNumbers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allNumbers.csv')

```

```{r, echo=FALSE, error=FALSE, message=FALSE,warning=FALSE}
library(tidyverse)
library(cowplot)
allShades %>%
  drop_na(name) %>%
  filter(str_detect(name,"Nude") 
         | str_detect(name, "nude") 
         | str_detect(description, "Nude") 
         | str_detect(description, "nude")) -> ShadesNude

ShadesNude %>%
  ggplot(aes(x = lightness, fill = hex)) +
  geom_dotplot(binpositions = "all", binwidth = 0.02,
               method = "histodot", stackgroups = TRUE) +
  theme_minimal() +
  theme(legend.position = "none") +
  scale_fill_identity()
```


## What I learnt

+ https://pudding.cool/2021/03/foundation-names/ This article raised awareness of usage of the word "Nude" in makeup foundation colors being potentially problematic, because it suggests a correlation between "Nude" and lighter shades of skin colors.
+ The plot on top is an illustration of "Nude" shade foundations relating with lightness of the color.
+ I learnt to use geom_dotplot for the case of single variable, and plot reassures the finding from the mentioned article.

## Codes

```{r, eval = FALSE, message=FALSE, error=FALSE}
sephora <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/sephora.csv')
ulta <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/ulta.csv')
allCategories <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allCategories.csv')
allShades <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allShades.csv')
allNumbers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-30/allNumbers.csv')

library(tidyverse)
library(cowplot)
allShades %>%
  drop_na(name) %>%
  filter(str_detect(name,"Nude") 
         | str_detect(name, "nude") 
         | str_detect(description, "Nude") 
         | str_detect(description, "nude")) -> ShadesNude

ShadesNude %>%
  ggplot(aes(x = lightness, fill = hex)) +
  geom_dotplot(binpositions = "all", binwidth = 0.02,
               method = "histodot", stackgroups = TRUE) +
  theme_minimal() +
  theme(legend.position = "none") +
  scale_fill_identity()
```
